---
title: "simulation_week6"
author: "Tingyu Zhu"
date: "11/2/2020"
output: pdf_document
---
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(purrr)
library(ggplot2)
library(here)
devtools::load_all()
set.seed(1222)
```

## Commonly used kernel functions

In the beta family kernel density, lambda=0,1,2,3 correspond to the uniform, the Epanech- nikov, the biweight, and the triweight kernel functions, respectively.  
```{r}
kernel_beta <- function(x,lambda){(1-x^2)^lambda*(abs(x)<=1)/beta(lambda+1,0.5)}

kernel_comp <- tibble(
  grid = seq(-3,3,by=0.1),
  Normal = dnorm(grid),
  Uniform = kernel_beta(grid,0),
  Epanechnikov = kernel_beta(grid,1),
  Biweight = kernel_beta(grid,2),
  Triweight = kernel_beta(grid,3)
  )

kernel_comp_long <- kernel_comp %>% 
  pivot_longer(c(`Normal`, `Uniform`,`Epanechnikov`,
                 `Biweight`,`Triweight`), names_to = "Kernel", values_to = "Density")


ggplot(data=kernel_comp_long) + 
  geom_line(aes(x = grid, y = Density, color = Kernel)) +
  labs(title = "Commonly used kernel functions") +
  theme_light() 
```


## Compute the MADE (Mean Absolute Deviation Errors)

The Mean Absolute Deviation Errors is a way to measure the bias of the KDE method. 
It is defined as $$MADE=\frac{1}{n}\sum_{k=1}^{n}|(\hat{f}(u_k)-f(u_k))|$$,
where $\hat{f}(u_k)$ is the kernel estimte of $f(u_k))$, and {$u_k$} are the grid points taken to be arbitrary within the range of data. Small MADE means the estimated densities is colse to the true densities. 

When the sample is generated from the known distribution like exp,beta, gamma, etc., we can use corresponding built-in functions (dexp(), dgamma, etc.) to calculated the true denstities of the grid points. If the sample is not from the familar distributions, we can use the built-in function "denstiy()" in R to get the value of $f(u_k))$s.

## Simulation 

Explore the simulation results with different sample sizes & kernels

### Build simulation functions that can save the MADE.

Note: The follwoing functions are similar to `kde_est_big`, `sim_big_made `, and `save_made ` that are used in week 7, which are listed in the `kde_est_functions.R`. However, they are the first versions and are much simpler. Thus, we will not modify this part and keep those fucntions here as the records.

Here `kde_n_ker_est()` is used to simulate over different sample size and kernels for a given bandwidth h=1.06*100^(-0.2), the output is the estimated densities. 

`sim_made` is used to first generate combination of parameters, and then for each combination of parameters, using `kde_n_ker_est()` to generate the estimated densities, and the corresponding true densities. Then, `made()` is used to computae the MADE. The out out is the MADEs under different combination of parameters.

```{r}
# Define some functions for gievn h=1.06*100^(-0.2), 

# simulate over different sample size and kernels
kde_n_ker_est <- function(x, n, ker, grid){
  # x large population
  # n sample sizes
  # ker name of kernels
  # grid grid points
  map2(.x = n, .y = ker, 
        ~KDE_est(sample(x, .x, replace = FALSE), 
                  grid, h= 1.06*100^(-0.2), ker = .y)$f_est)
}

sim_made <- function(ns, kes, x, grid, true_f){
  
  # generates every combination of parameters (ns:kers)
  simulation_params_big <- list(
  n = ns,
  kernel_type = kers)
  n_ker_est_big <- cross_df(simulation_params_big)
  
  
  n_ker_est_big <- n_ker_est_big %>% 
  mutate(
    # for each combination of the paras, using the kde_n_ker_est()
    f_ests = kde_n_ker_est(x, n, kernel_type, grid),
    f_true = map(1:length(n), ~true_f) # save the corresponding true density
  ) %>% 
  mutate(
    MADE = map2_dbl(.x = f_ests, .y = f_true, ~made(.x,.y)) # calculate the MADE
  )
  return(n_ker_est_big$MADE)
}

```


### Simulation
Generate samples from t(3) distribution. Then, using five types of kernel function and different size of samples that are drawn from the large population. 

Simulation is repeated `n.sim` times.
```{r}
# population
x <- rt(50000, df=3)

# simulaiton parameters
ns <- c(100, 500, 1000, 1500) # sample sizes
kers  <- c("normal", "uniform", "epanech", "biweight", "triweight") # kernel functions
grid <- seq(-5,15, 0.1)

# true density 
true_f <- dt(grid, df=3)

# simulation
n.sim <- 100 # number of replicates
sim_rlt <- map(1:n.sim, ~sim_made(ns, kers, x, grid,true_f))

```


### Save result
```{r}
made_mat <- matrix(unlist(sim_rlt), nrow = length(ns)*length(kers) )

made_comapre <- tibble(
  n =rep(ns, time=length(kers)),
  kernel_type = rep(kers, each=length(ns)),
  made_mean = apply(made_mat, 1, mean),
  made_sd = apply(made_mat, 1, sd)
)
write_rds(made_mat , here("results", "week6-sim.rds"))
write_rds(made_comapre, here("results", "week6-sim-plot.rds"))
```


### Analysis
Results and plots are documented in `Summary_week6` in the `analysis` file.